Generality in food webs scales with species richness, not latitude

### 2015-04-07 manuscript/latitudepaper.tex
A first stab at the discussion

The tendency of food-web structure to exhibit scaling relationships with
species richness has been well-established \citep{Dunne2004,Riede2010}. As
species richness in particular is also known to vary systematically over
latitude \citep{}, intuitively one might suspect that any relationship
between food-web properties such as generality might be due to the latitudinal
gradient in species richness. In this dataset, however, we did not find
overall latitudinal gradients in species richness, links per species, 
generality, or vulnerability.

The lack of latitudinal gradients in food-web properties in this dataset contrasts
strongly with other studies which have found consistent variation in species richness,
[[other properties]] \citep{}. As numbers of species and links included in a food web
vary strongly with sampling effort as well as with the underlying diversity of the study
area, it is possible that the lack of latitudinal trends here is a result of researchers
tending to expend similar amounts of sampling effort across studies. This could result in
food webs describing species-rich tropical communities omitting more species and links
than species-poor arctic communities. In addition, it is worth noting that gradients in
species richness are generally measured for a single taxonomic group at a time~\citep{}.
It is possible that these taxa are not well-represented in our food webs and that the
dominant taxa in them do not have an underlying latitudinal gradient in richness. In
either case, the lack of association between species richness
and latitude in any ecosystem type nevertheless means that any effect of latitude on scaling relationships
between species richness and other properties is not being driven by underlying variation in
species richness, allowing us to more clearly assess effects of latitude on scaling.

These effects varied strongly across ecosystem types. In marine and terrestrial food webs,
scaling of links per species, generality, and vulnerability was not strongly affected by
latitude. This is consistent with the idea that species' niche breadths do not vary systematically
with temperature and productivity but that the niche space might be larger in species-rich communities
~\citep{Davies2007}. In contrast, scaling in of lake, estuarine, and stream was generally stronger
towards the poles. [[Sentence structure in following?]] This means that species in tropical communities gain fewer additional feeding links
per additional species in the web, supporting the hypothesis that greater stability in the tropics
leads to narrower niches~\citep{Brown2004} and a higher proportion of specialists~\citep{}. As food webs
are generally aggregated in space and time, the greater increase in links in high latitude stream, 
estuarine, and lake food webs might reflect prey switching as different food sources become
available~\citep{}.

@@

Our results were consistent with the latitude-niche breadth hypothesis, but only in certain ecosystem
types. This suggests that different types of food webs respond differently to differences in climate
driven by latitudinal gradients. [[A sentence or two explaining why this is important.]]

>>>>

The tendency of food-web structure to exhibit scaling relationships with
species richness has been well-established \citep{Dunne2004,Riede2010}. As
species richness in particular is also known to vary systematically over
latitude \citep{}, intuitively one might suspect that any relationship
between food-web properties such as generality might be due to the latitudinal
gradient in species richness. In this dataset, however, we did not find
overall latitudinal gradients in species richness, links per species, 
generality, vulnerability, or the proportions of food webs accounted for by 
basal resources, intermediate consumers, and top predators.

The lack of latitudinal gradients in food-web properties in this dataset contrasts
strongly with other studies which have found consistent variation in species richness,
[[other properties]] \citep{}. As numbers of species and links included in a food web
vary strongly with sampling effort as well as with the underlying diversity of the study
area, it is possible that the lack of latitudinal trends here is a result of researchers
tending to expend similar amounts of sampling effort across studies. This could result in
food webs describing species-rich tropical communities omitting more species and links
than species-poor arctic communities. In addition, it is worth noting that gradients in
species richness are generally measured for a single taxonomic group at a time~\citep{}.
It is possible that these taxa are not well-represented in our food webs and that the
dominant taxa in them do not have an underlying latitudinal gradient in richness. In
either case, the lack of association between species richness
and latitude in any ecosystem type nevertheless means that any effect of latitude on scaling relationships
between species richness and other properties is not being driven by underlying variation in
species richness, allowing us to more clearly assess effects of latitude on scaling with 
species richness and proportions of species in different trophic levels.

Scaling of links per species, generality, and vulnerability with species
richness varied strongly across ecosystem types. In estuarine, marine, and
terrestrial food webs scaling of each property varied little with latitude.
This is consistent with the idea that species' niche breadths do not vary
systematically with temperature and productivity but that the niche space
might be larger in species-rich communities~\citep{Davies2007}. In lake food
webs, in contrast, scaling of each property was much stronger in high-latitude
food webs. In stream food webs, scaling of links per species and vulnerability
varied little over latitude while scaling of generality was stronger in high-
latitude food webs. This means that species in trophical freshwater
communities gain fewer additional feeding links per additional species in the
web and is consistent with the hypothesis that greater stability in the
tropics leads to narrower niches~\citep{Brown2004} and a higher proportion of
specialists~\citep{}.

In lake food webs, species in tropical food webs also gained fewer predators,
and therefore fewer links overall. Conversely, for species in high-latitude
food webs numbers of predators, prey, and links per species all increased
rapidly with increasing species richness. This may reflect prey switching as
different food sources become available in different seasons~\citep{}.
Alternatively, the sharper increases in links per species, generality, and
vulnerability at higher latitudes may be driven by the relationships between
each property and the proportion of basal resources in these food webs.
[[Except each property increases more with S and decreases more with B...]]

Surprisingly species in high-latitude stream food webs, while gaining many
additional prey species per additional species in the food web, did not
receive any more predators or links than species in low-latitude streams. The
limited influence of latitude on the scaling relationships of links per
species and vulnerability may be because, for these properties, latitude had
opposite effects on the scaling relationships with proportions of basal
resources and top predators. When considering generality, however, only the
proportion of basal resources varied significantly over latitude. [[Same
problem as in lakes, the trends are opposite.]]

@@

% Our results were consistent with the latitude-niche breadth hypothesis, but only in certain ecosystem
% types. This suggests that different types of food webs respond differently to differences in climate
% driven by latitudinal gradients. [[A sentence or two explaining why this is important.]]
